---
title: "`basiclm` Package Tutorial"
author: Haisheng Xu
date: "Dec. 1, 2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# Install package from GitHub
# devtools::install_github("haisx/basiclm")

# Load the package
library(basiclm)
```
There is one `linear_model()` function in the package. It presents some important statistics of linear regression model. 
The input variables should all be **numeric variables**.

## The Parameters of Function `linear_model`
`formula`: The formula of interests. It should follow the format of y~x. You can add more than one explanatory variables with different form like y~x+z+I(z^2).
**e.g.**. linear_model(y~x)

`data`: The name of the data needed to conduct the linear regression model. 
**e.g.** linear_model(y~x, data = mydata)

`digit`: The digits you want to keep in the output. The p-value would not be affected by `digit`. The default `digit` option is `digit` = 3.
**e.g.** linear_model(y~x, data = mydata, digit = 8)

`detailed`: The `detailed` means a detailed output of the linear regression model. The detailed table includes more information about coefficients and model like Std Error, t value of the coefficients, R-Squared of the model, and so on. The default `detail` = FALSE. 
**e.g.** linear_model(y~x, data = mydata, digit = 8, detailed = TRUE)


## Use `linear_model()` with Vectors
We can create our own response and explanatory variables and put them into the function.
```{r 0}
y = c(1:10)
x = c(2:5, 11:6)

linear_model(y~x)

```
we can get what we called in function and the coefficients of the linear regression model directly.

## Use `linear_model()` with Dataset
Here we use `iris` data as a simple example.
```{r 1}
head(iris)

# We will use the numeric variables in iris dataset
linear_model(Petal.Length~Sepal.Width ,data = iris)

# Keep more digits of results
linear_model(Petal.Length~Sepal.Width ,data = iris, digit = 8)
```

## Get Specific Output by Using `detailed` Option
```{r 2}
linear_model(Petal.Length~Sepal.Width ,data=iris, detailed = TRUE)

```

## Performance of `linear_model()` vs. `lm()`
```{r n}
set.seed(222)
testx = runif(5000000, 1, 10000)
testy = runif(5000000, 1, 10000)

system.time(lm(testy~testx))
system.time(linear_model(testy~testx))


set.seed(223)
testx = runif(5000000, 1, 10000)
testy = runif(5000000, 1, 10000)
testz = runif(5000000, 1, 10000)

system.time(lm(testz~ testx + testy))
system.time(linear_model(testz~ testx + testy))
```

## Output Comparisons `linear_model()` vs. `lm()`
```{r n2}
#iris sample data
linear_model(Petal.Length~Sepal.Width, data=iris, digit = 8, detailed = T)

summary(lm(Petal.Length~Sepal.Width, data=iris))

# Other random generated data
set.seed(2212)
testx = c(1:1000)
testy = runif(1000, 1, 10000)

linear_model(testy~testx, digit = 5, detailed = T)

summary(lm(testy~testx))
```
